A Roadmap for\\HEP Software and Computing R\&D\\for the 2020s

### 2018-11-06 CWP/papers/HSF-CWP-2017-01_roadmap/latex/cwp-main.tex
Consistent dates for short/long term software development goals
Add mention and references to GitHub and GitLab

To maximise productivity, it is very beneficial to use development tools
that are not HEP-specific. There are many open source projects that are
of similar scale to large experiment software stacks and standard tools
are usually well documented. For source control HEP has generally chosen
to move to \emph{git}~\cite{git},
which is very welcome, as it also brings an
alignment with many open source projects and commercial organisations.
Likewise, \emph{CMake}~\cite{CMake}
is widely used for the builds of software
packages, both within HEP and outside. Packaging many build products
together into a software stack is an area that still requires close
attention with respect to active developments (the HSF has an active
working group here).

@@

Ongoing activities and short-term projects, include the following:

@@

Medium term projects include the following:

>>>>

To maximise productivity, it is very beneficial to use development tools
that are not HEP-specific. There are many open source projects that are
of similar scale to large experiment software stacks and standard tools
are usually well documented. For source control HEP has generally chosen
to move to \emph{git}~\cite{git},
which is very welcome, as it also brings an
alignment with many open source projects and commercial organisations.
A major benefit that has come with this technical choice is the use
of social coding sites, such as \emph{GitHub} ~\cite{GitHub}
and \emph{GitLab}~\cite{GitLab}, where
code sharing and code review are far superior compared to previous
solutions.
Likewise, \emph{CMake}~\cite{CMake}
is widely used for the builds of software
packages, both within HEP and outside. Packaging many build products
together into a software stack is an area that still requires close
attention with respect to active developments (the HSF has an active
working group here).

@@

Ongoing activities and short-term projects, to complete by 2020,
include the following:

@@

Longer term projects, to conclude by 2022, include the following:
